Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
Copy-edit introduction

We chose to focus our study on security bugs rather than other types of
software defects. This is because compared to other bug categories,
the category of security bugs has two distinct features: it is critical~\cite{SZ12}
for an organization's infrastructure
and moreover it can cause significant financial damage to 
an organization~\cite{TH04}\cite{BCL08}\cite{R06}. 
Specifically, a software bug can
lead to a malfunction of a software artifact that runs under specific
requirements but a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain. In this case, such bugs could span a wide
range of security and privacy issues, like viewing sensitive information, the destruction or
modification of sensitive data, denial of service and others.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be to mitigate such bugs.

% @dimitro: say why we did this work, not how we did it
The motivation behind our work was to validate whether programmers care for
such high-risk bugs when they release a new version of their software. In
addition, we wanted to investigate other critical features associated with such
vulnerabilities like the persistence of a bug; in essence, to check if critical bugs stay
unresolved for a long time. Also, we wanted to elaborate more on the relation of security
bugs not only with performance bugs (as Zaman et al.~\cite{ZAH11} have already
done) but also with other bug categories. In the same manner, we tried to check
the relation between version size and security bugs, knowing the
that research has been contradictory on the the
issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
Finally, we examined the Maven ecosystem as a whole from a security
perspective. Its structure gave us the opportunity to see if a project version that is a dependency to
a large number of others contains a low rate of security bugs~\cite{MW10}.
%In this case we can strengthen the relationship between Linus' Law and
%software security as Meneely et al. have already indicated~\cite{MW10}.

In this work we:
\begin{itemize}
	\item Analyze how security bugs found through static analysis
evolve over time. To achieve this, we inspected every project per version.
Our hypothesis is that security bugs should decrease as a project evolves since
they are critical and developers should eliminate them.
%We present evidence that defect counts remain relatively stable
%across project revisions.
	\item Examine security bug persistence between versions. 
We expect that security bugs should be eliminated earlier than other bugs.
%We find that a specific defect remains unfixed on average 
%for 3 revisions.
	\item Study the relation between security bugs and a project
version's size. Our hypothesis is that security bugs are proportional to a project
version's size. Here, size is defined in terms of bytecode.
%We show that many defect types are correlated with the project's
%size (with the notable exception of high-risk security defects).
	\item Examine the correlation of security bugs with other bug categories.
Our hypothesis is that security bugs flock together with bugs that
have to do with performance, coding practices and others.
%We show that a code base can have defect hotspots.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
  %\item Make available a carefully constructed dataset and a statistical toolkit for
   % performing analysis of the Java Maven ecosystem.
\end{itemize}

>>>>

We chose to focus our study on security bugs rather than other types of
software defects. This is because compared to other bug categories,
failures due to security bugs have two distinct features:
they can severeyl affect an organization's infrastructure\cite{SZ12}, and
they can cause significant financial damage to
an organization~\cite{TH04}\cite{BCL08}\cite{R06}. 
Specifically,
whereas a software bug can cause a software artifact to fail,
a security bug can allow a malicious user to alter the execution
of the entire application for his or her own gain.
In this case, such bugs could give rise to a wide
range of security and privacy issues, like
the access of sensitive information,
the destruction or modification of data, and
denial of service.
Moreover, security bug disclosures lead to a negative and significant change
in market value for a software vendor~\cite{TW07}.
Hence, one of the basic pursuits in every new software release should
be to mitigate such bugs.

% @dimitro: say why we did this work, not how we did it
The motivation behind our work was to validate whether programmers care for
the risk posed by security bugs when they release a new version of their software.
In addition, we wanted to investigate other critical features associated with such
vulnerabilities like the persistence of a bug;
in essence, to see whether critical bugs stay unresolved for a long time.
Also, we wanted to elaborate more on the relation of security
bugs with other bug categories.
In the same manner, we tried to looked at the relationship
between successive product versions and the number of security bugs,
knowing the that research has produced contradictory results on this
issue~\cite{BP84}\cite{SYTP85}\cite{NBZ06}\cite{GKMS00}.
Finally, we examined the Maven ecosystem as a whole from a security
perspective. Its structure gave us the opportunity to see if a project version that is a dependency to
a large number of others contains a low rate of security bugs~\cite{MW10}.
%In this case we can strengthen the relationship between Linus' Law and
%software security as Meneely et al. have already indicated~\cite{MW10}.

In this work we:
\begin{itemize}
	\item Analyze how security bugs found through static analysis
evolve over time. To achieve this, we inspected all releases of every project.
Our hypothesis is that security bugs should decrease as a project evolves,
for they form critical issues, which developers should eliminate.
%We present evidence that defect counts remain relatively stable
%across project revisions.
	\item Examine security bug persistence across releases. 
We expect that security bugs should be eliminated earlier than other bugs.
%We find that a specific defect remains unfixed on average 
%for 3 revisions.
	\item Study the relation between security bugs and a project
release's size. Our hypothesis is that security bugs are proportional to a project
release's size (defined in terms of bytecode size).
%We show that many defect types are correlated with the project's
%size (with the notable exception of high-risk security defects).
	\item Examine the correlation of security bugs with other bug categories.
Our hypothesis is that security bugs appear together with bugs that
are related with performance, coding practices, and product stability.
%We show that a code base can have defect hotspots.
%	\item The relation of software dependencies and security bugs. Our
%hypothesis is that an artifact that is a dependency of many other artifacts
%should have a low rate of security bugs. 
  %\item Make available a carefully constructed dataset and a statistical toolkit for
   % performing analysis of the Java Maven ecosystem.
\end{itemize}
